---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ogreleases

<!-- badges: start -->
<!-- badges: end -->

A selection of Government of Ontario press releases scraped from the [Ontario Newsroom](https://news.ontario.ca/en/). This information is © Queen's Printer for Ontario, 2020, and is to be used for teaching and research.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chris31415926535/ogreleases")
```
## Example

This example shows how to load the data, count the number of press releases from each source, and plot the results:

```{r example, message=FALSE}
library(tidyverse)
library(ogreleases)

## load the data

df <- ogreleases::ogreleases_data

# who issued the most press releases?
df %>%
  group_by(issuer) %>%
  summarise(count=n()) %>%
  ggplot() +
    geom_col(aes(x=reorder(issuer, count), y=count)) +
    coord_flip() +
    theme_minimal() +
    labs(
      title="Press Releases by Source, Jan 2019 - Sept 2020",
      x=NULL, y = NULL
    )
```
